explore networkx

### 2019-12-16 scripts/explore-networkx.Rmd
fst multiNetX

```{python}
import pandas as pd
import networkx as nx

edges = pd.read_csv('../data/edgels.csv')
edges
G=nx.from_pandas_edgelist(edges, 'V1', 'V2', edge_attr='w')
```

>>>>

```{python}
import pandas as pd
import networkx as nx
import multiNetX as ml

edges = pd.read_csv('../data/edgels.csv')
edges
G=nx.from_pandas_edgelist(edges, 'V1', 'V2', edge_attr='w')

```
